\thispagestyle{empty}

\vspace*{\fill}

\noindent \textit{The GoGreenGuide is a strategy for iGEM teams to make a positive, real world, environmental impact as they perform their synthetic biology project team work. The guide contains practical advice designed to meet all aspects of this goal. Sustainable solutions are presented for optimal laboratory energy use, waste management and sustainable procurement. Tools are included to enable tracking of sustainable lab bench work goals, such as how to calculate a team's greenhouse gas footprint to offset travel emissions. The guide also explains how to join iGEM Goes Green and how to inspire others by planning green meetups, organized events and spreading the word online. The combination of knowledge and methods within this publication promotes all sustainable lab bench work.} \\

\noindent \textit{The thousands of iGEM synthetic biologists worldwide have the opportunity to make a giant impact by joining iGEM goes green. The input and collaboration of many teams will continually improve this resource. Please use and share this guide to help put sustainable ideals into sustainable actions.} \\

Nicole Kelesoglu, Editor and blogger of Labconscious, an open resource website for scientists in green lab initiatives \\\bigskip
 \\\bigskip
 \\\bigskip

\noindent \textit{Both financial and non-financial value drivers contribute to companies' success. Identifying interdependencies between value drivers and consequently deduce specific measures to increase the positive impact of ecologic actions and decrease negatives ones are important cornerstones of a sustainable development.} \\
	
	
\noindent \textit{In this context, measuring and evaluating sustainability with various methods provides important information on the base of which decision can be made.} \\


\noindent \textit{Synthetic biology and its different focuses can achieve important contributions to sustainable development, particularly regarding the reduction of greenhouse gases. The development of novel processes should always be carried out in context of evaluation of sustainability.} \\\bigskip


Peter Saling, BASF SE, Director Sustainability Methods


\vspace*{\fill}